---
title: "Lab 00 - Hello IDS!"
author: "Gregor Mackay"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Cameron", "Jamie", 
           "Benji", "Tom", "Max"),
  github_username = c("mcgregors-garden", "Carthur7777", "jd43", 
                      "BenjiEdmondson", "tomdsimpson", "maxx-creed"), 
  colour = c("powderblue", "navyblue", "purple", 
             "thistle3", "cadetblue3", "olivedrab"),
  hobby = c("Hopping", "rugby", "taekwondo", 
            "orienteering", "cycling", "guitar"),
  favourite_number = c(2, 7, 5, 9, 3,4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

a bar graph of my teams favourite numbers (benji won)

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favourite Number",
          title = "My Teams Favourite Number")
```

Labs adds label to graphs axis

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

This would be a bad way of displaying data for the whole class as the bar graph would be very large, a pie chart would be a better visualisation
